Livin' on the edge: Precision yield data shows evidence of ecosystem services from field boundaries

### 2021-11-04 Manuscript/manuscript.Rmd
Updated manuscript for submission

bibliography: yieldRefs.bib
geometry: "left=3cm,right=3cm,top=3cm,bottom=3cm"
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    toc: false
    fig_caption: true
    highlight: haddock
csl: ecology-letters.csl    
header-includes:
  \makeatletter \def\ps@pprintTitle{  \let\@oddhead\@empty  \let\@evenhead\@empty  \def\@oddfoot{\centerline{\thepage}} \let\@evenfoot\@oddfoot} \makeatother
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{setspace}
  %\linenumbers

@@

@@

\newpage
<!-- \doublespacing -->
\onehalfspacing

@@

Intensive agricultural production has increased over the last 100 years, and agricultural land now makes up over a third of ice-free land on Earth [@ramankutty2018].
This has allowed increases in human population and increased global stability in production [@foley2011].
However, this is not without cost, as higher-diversity non-crops are converted to lower-diversity crops, resulting in loss of habitat and overall biodiversity of non-target organisms.
Maintaining both biodiversity and production in agroecosystems represents a goal of conservationists and agronomists, and holds the potential for win-win scenarios ["multifunctionality" _sensu_ @mitchell2014; @frei2018].
Key to this goal is the preservation of semi-natural land (SNL) in and around crops, which represents the interface between crops and non-crops within agroecosystems.

@@

Precision yield data were collected directly from farmers across Alberta.
Farmers were solicited for yield data through local agronomists, and we received `r nrow(datSource)` field-years of data from `r length(unique(datSource$grower))` growers across a total of `r length(unique(datSource$year))` years (`r min(unique(datSource$year))`-`r max(unique(datSource$year))`).
We converted raw data to a standard csv format using Ag Leader SMS®.
`r round(100*sum(grepl('(Wheat|Canola|Peas)',datSource$crop))/nrow(datSource))`% of the crop types where either wheat (_Triticum aestivum_), canola (_Brassica napus_), or peas (_Pisum sativum_), three of the most common crops in rotation in Alberta [@statscan_canola2014].
The remaining crop types had low replication, so we constrained our analysis to only field-years containing wheat (`r sum(datSourceFinal$crop=='Wheat')`), canola (`r sum(datSourceFinal$crop=='Canola')`), or peas (`r sum(datSourceFinal$crop=='Peas')`), for a total of `r nrow(datSourceFinal)` field-years of data.
Individual fields contained between `r min(yearsPerField)` and `r max(yearsPerField)` years of data (mean: `r round(mean(yearsPerField),1)`), containing a total of `r round(sum(datSourceFinal$npoints)/1e6,1)` million data points.

@@

<!-- For example, average canola yield was about 0.5 T/ha lower close to Standard field edges, and yield SD was about 0.3 T/ha SD higher. -->
Wheat and shelterbelts aside, why did we find few consistent effects of boundary type on crop yield?
Our work examined only the first and last links in the causal chain _Field Boundary_ $\rightarrow$ _Ecosystem Service_ $\rightarrow$ _Crop Yield_, meaning that are two mediating relationships where the overall relationship could be broken or obscured.
First, field boundaries may not have any influence on beneficial insect abundance if separated from the larger landscape context, or spillover of beneficial organisms may be low.
Second, beneficial insect abundance may not influence crop yield if pest pressure or pollination deficits are low, which may vary among year or location.
<!-- However, our work does show that precision yield data could easily be joined to data on insect abundance to model this more completely. -->
Abiotic ecosystem services, such as reduced wind speed or temperature, also depend on the structure of the boundary and whether wind or temperature are limiting crop production.
Our work suggests that we need to better examine the context in which a) beneficial organisms spillover from field boundaries and b) under what conditions field boundaries provide tangible ecosystem services.
We consider these reasons below:

@@

# Author Contributions

SVJR, LHN, and PG conceived of the project.
SVJR collected data, conducted analysis, and wrote the manuscript.

@@

We thank Trent Clark, Dean Hubbard, Alvin French, and Kristina Polziehn for providing yield data for us, and providing insight on their yield data. 
We also thank Autumn Barnes and Keith Gabert of the Canola Council of Canada, and Laurel Thompson and JP Pettyjohn of Lakeland College for connecting us with farmers and agronomists.
Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and Waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, and the Alberta Conservation Association.

>>>>

bibliography: yieldRefs.bib
geometry: "left=3cm,right=3cm,top=3cm,bottom=3cm"
output: 
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    toc: false
    fig_caption: true
    highlight: haddock
csl: ecology-letters.csl    
header-includes:
  \makeatletter \def\ps@pprintTitle{  \let\@oddhead\@empty  \let\@evenhead\@empty  \def\@oddfoot{\centerline{\thepage}} \let\@evenfoot\@oddfoot} \makeatother
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{setspace}
  \linenumbers

@@

fieldAreas <- sapply(paste0('.',datSource$boundaryPath),function(x){
  require(sf)
  read_sf(x) %>% st_area() %>% sum()/10000 #Field areas in hectares
})

@@

\newpage
\doublespacing
<!-- \onehalfspacing -->

@@

Intensive agricultural production has increased over the last 100 years, and agricultural land now makes up over a third of ice-free land on Earth [@ramankutty2018].
This has allowed increases in human population and increased global stability in production [@foley2011].
However, this is not without cost, as higher-diversity non-crops are converted to lower-diversity crops, resulting in loss of habitat and overall biodiversity of non-target organisms.
Maintaining both biodiversity and production in agroecosystems represents a goal of conservationists and agronomists, and holds the potential for win-win scenarios ["multifunctionality" _sensu_ @mitchell2014; @frei2018; but see also @karp2018].
Key to this goal is the preservation of semi-natural land (SNL) in and around crops, which represents the interface between crops and non-crops within agroecosystems.

@@

Precision yield data were collected directly from farmers across Alberta.
Farmers were solicited for yield data through local agronomists, and we received `r nrow(datSource)` field-years of data from `r length(unique(datSource$grower))` growers across a total of `r length(unique(datSource$year))` years (`r min(unique(datSource$year))`-`r max(unique(datSource$year))`).
We converted raw data to a standard csv format using Ag Leader SMS®.
`r round(100*sum(grepl('(Wheat|Canola|Peas)',datSource$crop))/nrow(datSource))`% of the crop types where either wheat (_Triticum aestivum_), canola (_Brassica napus_), or peas (_Pisum sativum_), three of the most common crops in rotation in Alberta [@statscan_canola2014].
The remaining crop types had low replication, so we constrained our analysis to only field-years containing wheat (`r sum(datSourceFinal$crop=='Wheat')`), canola (`r sum(datSourceFinal$crop=='Canola')`), or peas (`r sum(datSourceFinal$crop=='Peas')`), for a total of `r nrow(datSourceFinal)` field-years of data.
Individual fields ranged from `r round(min(fieldAreas),1)` to `r round(max(fieldAreas),1)` ha in area (mean: `r round(mean(fieldAreas),1)` ha), and contained between `r min(yearsPerField)` and `r max(yearsPerField)` years of data (mean: `r round(mean(yearsPerField),1)`), for a total of `r round(sum(datSourceFinal$npoints)/1e6,1)` million data points.

@@

<!-- For example, average canola yield was about 0.5 T/ha lower close to Standard field edges, and yield SD was about 0.3 T/ha SD higher. -->
Wheat and shelterbelts aside, why did we find few consistent effects of boundary type on crop yield?
Our work examined only the first and last links in the causal chain _Field Boundary_ $\rightarrow$ _Ecosystem Service_ $\rightarrow$ _Crop Yield_, meaning that are two mediating relationships where the overall relationship could be broken or obscured.
First, field boundaries may not have any influence on beneficial insect abundance if separated from the larger landscape context, or spillover of beneficial organisms may be low.
Second, beneficial insect abundance may not influence crop yield if pest pressure or pollination deficits are low, which may vary among year or location.
<!-- However, our work does show that precision yield data could easily be joined to data on insect abundance to model this more completely. -->
Abiotic ecosystem services, such as reduced wind speed or temperature, also depend on the structure of the boundary and whether wind or temperature are limiting crop production.
Our work suggests that we need to better examine the context in which a) beneficial organisms spillover from field boundaries and b) under what conditions field boundaries provide tangible ecosystem services [@karp2018].
We consider these reasons below:

@@

<!-- # Author Contributions -->

<!-- SVJR, LHN, and PG conceived of the project. -->
<!-- SVJR collected data, conducted analysis, and wrote the manuscript. -->

@@

We thank Trent Clark, Dean Hubbard, Alvin French, and Kristina Polziehn for providing yield data for us, and providing insight on their yield data. 
We also thank Autumn Barnes and Keith Gabert of the Canola Council of Canada, and Laurel Thompson and JP Pettyjohn of Lakeland College for connecting us with farmers and agronomists.

# Funding Sources

Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and Waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, and the Alberta Conservation Association.

### 2021-11-04 Manuscript/manuscript.tex
Updated manuscript for submission

% Pandoc header
\makeatletter \def\ps@pprintTitle{  \let\@oddhead\@empty  \let\@evenhead\@empty  \def\@oddfoot{\centerline{\thepage}} \let\@evenfoot\@oddfoot} \makeatother \usepackage{float} \floatplacement{figure}{H} \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} \usepackage{setspace} %\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\onehalfspacing

@@

Intensive agricultural production has increased over the last 100 years, and agricultural land now makes up over a third of ice-free land on Earth (Ramankutty \emph{et al.} 2018).
This has allowed increases in human population and increased global stability in production (Foley \emph{et al.} 2011).
However, this is not without cost, as higher-diversity non-crops are converted to lower-diversity crops, resulting in loss of habitat and overall biodiversity of non-target organisms.
Maintaining both biodiversity and production in agroecosystems represents a goal of conservationists and agronomists, and holds the potential for win-win scenarios ({``multifunctionality''} \emph{sensu} Mitchell \emph{et al.} 2014; Frei \emph{et al.} 2018).
Key to this goal is the preservation of semi-natural land (SNL) in and around crops, which represents the interface between crops and non-crops within agroecosystems.

@@

Precision yield data were collected directly from farmers across Alberta.
Farmers were solicited for yield data through local agronomists, and we received 298 field-years of data from 5 growers across a total of 7 years (2014-2020).
We converted raw data to a standard csv format using Ag Leader SMS®.
85\% of the crop types where either wheat (\emph{Triticum aestivum}), canola (\emph{Brassica napus}), or peas (\emph{Pisum sativum}), three of the most common crops in rotation in Alberta (Statistics Canada 2014).
The remaining crop types had low replication, so we constrained our analysis to only field-years containing wheat (94), canola (119), or peas (39), for a total of 252 field-years of data.
Individual fields contained between 1 and 6 years of data (mean: 3.1), containing a total of 14.4 million data points.

@@

Wheat and shelterbelts aside, why did we find few consistent effects of boundary type on crop yield?
Our work examined only the first and last links in the causal chain \emph{Field Boundary} \(\rightarrow\) \emph{Ecosystem Service} \(\rightarrow\) \emph{Crop Yield}, meaning that are two mediating relationships where the overall relationship could be broken or obscured.
First, field boundaries may not have any influence on beneficial insect abundance if separated from the larger landscape context, or spillover of beneficial organisms may be low.
Second, beneficial insect abundance may not influence crop yield if pest pressure or pollination deficits are low, which may vary among year or location.
Abiotic ecosystem services, such as reduced wind speed or temperature, also depend on the structure of the boundary and whether wind or temperature are limiting crop production.
Our work suggests that we need to better examine the context in which a) beneficial organisms spillover from field boundaries and b) under what conditions field boundaries provide tangible ecosystem services.
We consider these reasons below:

@@

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

SVJR, LHN, and PG conceived of the project.
SVJR collected data, conducted analysis, and wrote the manuscript.

@@

We thank Trent Clark, Dean Hubbard, Alvin French, and Kristina Polziehn for providing yield data for us, and providing insight on their yield data.
We also thank Autumn Barnes and Keith Gabert of the Canola Council of Canada, and Laurel Thompson and JP Pettyjohn of Lakeland College for connecting us with farmers and agronomists.
Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and Waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, and the Alberta Conservation Association.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-AAFC_data}{}%
Agriculture and Agri-Food Canada. (2018). \emph{{Annual Crop Inventory}}. Available at: \url{https://open.canada.ca/data/en/dataset/ba2645d5-4458-414d-b196-6303ac06c1c9}. Last accessed.

\leavevmode\hypertarget{ref-albrecht2020}{}%
Albrecht, M., Kleijn, D., Williams, N.M., Tschumi, M., Blaauw, B.R., Bommarco, R., \emph{et al.} (2020). The effectiveness of flower strips and hedgerows on pest control, pollination services and crop yield: A quantitative synthesis. \emph{Ecology Letters}.

@@

\leavevmode\hypertarget{ref-bao2012}{}%
Bao, Y., Li, H. \& Zhao, H. (2012). Effect of shelterbelts on winter wheat yields in sanded farmland of north-western shandong province, china. \emph{Journal of Food Agriculture \& Environment}, 10, 1399--1403.

@@

\leavevmode\hypertarget{ref-gardner2021}{}%
Gardner, E., Breeze, T.D., Clough, Y., Smith, H.G., Baldock, K.C.R., Campbell, A., \emph{et al.} (2021). Field boundary features can stabilise bee populations and the pollination of mass-flowering crops in rotational systems. \emph{Journal of Applied Ecology}, In press.

@@

\leavevmode\hypertarget{ref-griffin2007}{}%
Griffin, T.W., Brown, J.P. \& Lowenberg-DeBoerc, J. (2007). \emph{Yield monitor data analysis protocol: A primer in the management and analysis of precision agriculture data}.

@@

@@

\leavevmode\hypertarget{ref-lowe2021}{}%
Lowe, E.B., Groves, R. \& Gratton, C. (2021). Impacts of field-edge flower plantings on pollinator conservation and ecosystem service delivery {{}} a meta-analysis. \emph{Agriculture, Ecosystems {\&} Environment}, 310, 107290.

\leavevmode\hypertarget{ref-marja2019}{}%
Marja, R., Kleijn, D., Tscharntke, T., Klein, A.-M., Frank, T. \& Batáry, P. (2019). Effectiveness of agri-environmental management on pollinators is moderated more by ecological contrast than by landscape structure or land-use intensity. \emph{Ecology Letters}, In press.

@@

\leavevmode\hypertarget{ref-nguyen2021}{}%
Nguyen, L.H., Robinson, S.V.J. \& Galpern, P. (2021). Medium-resolution multispectral satellite imagery in precision agriculture: Mapping precision canola (\emph{brassica napus} {L.}) Yield using {Sentinel-2} time series. \emph{Precision Agriculture}, In Review (Preprint: https://www.essoar.org/doi/10.1002/essoar.10507479.2).

@@

\leavevmode\hypertarget{ref-singh1999}{}%
Singh, H.P., Kohli, R.K. \& Batish, D.R. (1999). Impact of \emph{populus deltoides} and \emph{dalbergia sissoo} shelterbelts on wheat {}a comparative study. \emph{International Tree Crops Journal}, 10, 51--60.

@@

\leavevmode\hypertarget{ref-weninger2021}{}%
Weninger, T., Scheper, S., Lackóová, L., Kitzler, B., Gartner, K., King, N.W., \emph{et al.} (2021). Ecosystem services of tree windbreaks in rural landscapes -- a systematic review. \emph{Environmental Research Letters}, In press.

@@

\CommentTok{\#Uses thin{-}plate splines with extra shrinkage (bs = \textquotesingle{}ts\textquotesingle{}), with 5 basis}
\CommentTok{\#functions for distance smoothers and 80 basis functions for spatial smoothers}

\CommentTok{\#Variance smoother}
\NormalTok{f2 }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}\textasciitilde{} s(dist,k=5,bs="ts",by=boundaryType) + s(E,N,k=80)\textquotesingle{}} 
\CommentTok{\#Means smoother}
\NormalTok{f }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}sqrt(DryYield)\textasciitilde{} s(dist,k=5,bs="ts",by=boundaryType) + s(E,N,k=80)\textquotesingle{}}\ErrorTok{)} 
\CommentTok{\#Combine into a list}
\NormalTok{flist }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}\FunctionTok{as.formula}\NormalTok{(f),}\FunctionTok{as.formula}\NormalTok{(f2)) }

>>>>

% Pandoc header
\makeatletter \def\ps@pprintTitle{  \let\@oddhead\@empty  \let\@evenhead\@empty  \def\@oddfoot{\centerline{\thepage}} \let\@evenfoot\@oddfoot} \makeatother \usepackage{float} \floatplacement{figure}{H} \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}} \usepackage{setspace} \linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\newpage
\doublespacing

@@

Intensive agricultural production has increased over the last 100 years, and agricultural land now makes up over a third of ice-free land on Earth (Ramankutty \emph{et al.} 2018).
This has allowed increases in human population and increased global stability in production (Foley \emph{et al.} 2011).
However, this is not without cost, as higher-diversity non-crops are converted to lower-diversity crops, resulting in loss of habitat and overall biodiversity of non-target organisms.
Maintaining both biodiversity and production in agroecosystems represents a goal of conservationists and agronomists, and holds the potential for win-win scenarios ({``multifunctionality''} \emph{sensu} Mitchell \emph{et al.} 2014; Frei \emph{et al.} 2018; but see also Karp \emph{et al.} 2018).
Key to this goal is the preservation of semi-natural land (SNL) in and around crops, which represents the interface between crops and non-crops within agroecosystems.

@@

Precision yield data were collected directly from farmers across Alberta.
Farmers were solicited for yield data through local agronomists, and we received 298 field-years of data from 5 growers across a total of 7 years (2014-2020).
We converted raw data to a standard csv format using Ag Leader SMS®.
85\% of the crop types where either wheat (\emph{Triticum aestivum}), canola (\emph{Brassica napus}), or peas (\emph{Pisum sativum}), three of the most common crops in rotation in Alberta (Statistics Canada 2014).
The remaining crop types had low replication, so we constrained our analysis to only field-years containing wheat (94), canola (119), or peas (39), for a total of 252 field-years of data.
Individual fields ranged from 5.9 to 369 ha in area (mean: 72.2 ha), and contained between 1 and 6 years of data (mean: 3.1), for a total of 14.4 million data points.

@@

Wheat and shelterbelts aside, why did we find few consistent effects of boundary type on crop yield?
Our work examined only the first and last links in the causal chain \emph{Field Boundary} \(\rightarrow\) \emph{Ecosystem Service} \(\rightarrow\) \emph{Crop Yield}, meaning that are two mediating relationships where the overall relationship could be broken or obscured.
First, field boundaries may not have any influence on beneficial insect abundance if separated from the larger landscape context, or spillover of beneficial organisms may be low.
Second, beneficial insect abundance may not influence crop yield if pest pressure or pollination deficits are low, which may vary among year or location.
Abiotic ecosystem services, such as reduced wind speed or temperature, also depend on the structure of the boundary and whether wind or temperature are limiting crop production.
Our work suggests that we need to better examine the context in which a) beneficial organisms spillover from field boundaries and b) under what conditions field boundaries provide tangible ecosystem services (Karp \emph{et al.} 2018).
We consider these reasons below:

@@

@@

We thank Trent Clark, Dean Hubbard, Alvin French, and Kristina Polziehn for providing yield data for us, and providing insight on their yield data.
We also thank Autumn Barnes and Keith Gabert of the Canola Council of Canada, and Laurel Thompson and JP Pettyjohn of Lakeland College for connecting us with farmers and agronomists.

\hypertarget{funding-sources}{%
\section{Funding Sources}\label{funding-sources}}

Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and Waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, and the Alberta Conservation Association.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-AAFC_data}{}%
Agriculture and Agri-Food Canada. (2018). \emph{{Annual Crop Inventory}}. Available at: \url{https://open.canada.ca/data/en/dataset/ba2645d5-4458-414d-b196-6303ac06c1c9}. Last accessed 6 February 2019.

\leavevmode\hypertarget{ref-albrecht2020}{}%
Albrecht, M., Kleijn, D., Williams, N.M., Tschumi, M., Blaauw, B.R., Bommarco, R., \emph{et al.} (2020). The effectiveness of flower strips and hedgerows on pest control, pollination services and crop yield: A quantitative synthesis. \emph{Ecology Letters}, 23, 1488--1498.

@@

\leavevmode\hypertarget{ref-bao2012}{}%
Bao, Y., Li, H. \& Zhao, H. (2012). Effect of shelterbelts on winter wheat yields in sanded farmland of north-western {Shandong} province, {China}. \emph{Journal of Food Agriculture \& Environment}, 10, 1399--1403.

@@

\leavevmode\hypertarget{ref-gardner2021}{}%
Gardner, E., Breeze, T.D., Clough, Y., Smith, H.G., Baldock, K.C.R., Campbell, A., \emph{et al.} (2021). Field boundary features can stabilise bee populations and the pollination of mass-flowering crops in rotational systems. \emph{Journal of Applied Ecology}, 58, 2287--2304.

@@

\leavevmode\hypertarget{ref-griffin2007}{}%
Griffin, T.W., Brown, J.P. \& Lowenberg-DeBoerc, J. (2007). \emph{Yield monitor data analysis protocol: A primer in the management and analysis of precision agriculture data}. SSRN.

@@

\leavevmode\hypertarget{ref-karp2018}{}%
Karp, D.S., Chaplin-Kramer, R., Meehan, T.D., Martin, E.A., DeClerck, F., Grab, H., \emph{et al.} (2018). Crop pests and predators exhibit inconsistent responses to surrounding landscape composition. \emph{Proceedings of the National Academy of Sciences}, 115, E7863--E7870.

@@

\leavevmode\hypertarget{ref-lowe2021}{}%
Lowe, E.B., Groves, R. \& Gratton, C. (2021). Impacts of field-edge flower plantings on pollinator conservation and ecosystem service delivery -- a meta-analysis. \emph{Agriculture, Ecosystems {\&} Environment}, 310, 107290.

\leavevmode\hypertarget{ref-marja2019}{}%
Marja, R., Kleijn, D., Tscharntke, T., Klein, A.-M., Frank, T. \& Batáry, P. (2019). Effectiveness of agri-environmental management on pollinators is moderated more by ecological contrast than by landscape structure or land-use intensity. \emph{Ecology Letters}, 22, 1493--1500.

@@

\leavevmode\hypertarget{ref-nguyen2021}{}%
Nguyen, L.H., Robinson, S.V.J. \& Galpern, P. (2021). Medium-resolution multispectral satellite imagery in precision agriculture: Mapping precision canola ({\emph{Brassica napus}} {L.}) Yield using {Sentinel-2} time series. \emph{Precision Agriculture}, In Review (Preprint: https://www.essoar.org/doi/10.1002/essoar.10507479.2).

@@

\leavevmode\hypertarget{ref-singh1999}{}%
Singh, H.P., Kohli, R.K. \& Batish, D.R. (1999). Impact of {\emph{Populus deltoides}} and {\emph{Dalbergia sissoo}} shelterbelts on wheat {}a comparative study. \emph{International Tree Crops Journal}, 10, 51--60.

@@

\leavevmode\hypertarget{ref-weninger2021}{}%
Weninger, T., Scheper, S., Lackóová, L., Kitzler, B., Gartner, K., King, N.W., \emph{et al.} (2021). Ecosystem services of tree windbreaks in rural landscapes -- a systematic review. \emph{Environmental Research Letters}, 16, 103002.

@@

\CommentTok{\#Uses thin{-}plate splines with extra shrinkage (bs = \textquotesingle{}ts\textquotesingle{}), with 5 basis}
\CommentTok{\#functions for distance smoothers and 80 basis functions for spatial smoothers}
\CommentTok{\#(see Wood 2017 for more details)}

\CommentTok{\#Variance smoothers}
\NormalTok{f2 }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}\textasciitilde{} s(dist,k=5,bs="ts",by=boundaryType) + s(E,N,k=80)\textquotesingle{}} 
\CommentTok{\#Mean smoothers}
\NormalTok{f }\OtherTok{\textless{}{-}} \StringTok{\textquotesingle{}sqrt(DryYield)\textasciitilde{} s(dist,k=5,bs="ts",by=boundaryType) + s(E,N,k=80)\textquotesingle{}}\ErrorTok{)} 
\CommentTok{\#Combine into a list}
\NormalTok{flist }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}\FunctionTok{as.formula}\NormalTok{(f),}\FunctionTok{as.formula}\NormalTok{(f2)) }
